The \dealii Library, Version 9.7

### 2025-07-28 9.7/paper.tex
Add a couple of fixes.

Classes derived from the \texttt{Mapping} base class are used to
represent the transformation from a reference cell (such as the unit
square or reference triangle) to a concrete cell that is part of a mesh.
\dealii has supported simplex and mixed meshes since the 9.3
release~\cite{changes93}. That release included \texttt{MappingFE}, a
\texttt{Mapping} class that uses the shape functions of a finite
element to implement this transformation; many common mappings can be
written in this way, and the class works with a variety of different elements by
delegating most computations to a provided \texttt{FiniteElement}
object. For example, the common bi-/trilinear mappings for quadrilaterals and
hexahedra, as well as the linear mappings on triangles and simplices,
can be implemented using \texttt{MappingFE} along with the
\texttt{FE\_Q} or \texttt{FE\_SimplexP} classes.

@@

\todo[inline]{Now
  bundling Kokkos 4.5.1; are we using something new from Kokkos? magic\_enum}

>>>>

Classes derived from the \texttt{Mapping} base class are used to
represent the transformation from a reference cell (such as the unit
square or reference triangle) to a concrete cell that is part of a mesh.
\dealii has supported simplex and mixed meshes since the 9.3
release~\cite{dealii93}. That release included \texttt{MappingFE}, a
\texttt{Mapping} class that uses the shape functions of a finite
element to implement this transformation; many common mappings can be
written in this way, and the class works with a variety of different elements by
delegating most computations to a provided \texttt{FiniteElement}
object. For example, the common bi-/trilinear mappings for quadrilaterals and
hexahedra, as well as the linear mappings on triangles and simplices,
can be implemented using \texttt{MappingFE} along with the
\texttt{FE\_Q} or \texttt{FE\_SimplexP} classes.

@@

\todo[inline]{Now
  bundling Kokkos 4.5.1; are we using something new from Kokkos?}
